\newpage
% =====================================================================
\section{Solving Multidimensional Problems: Dimensional Splitting}
\label{chap:dimensional-splitting}
% =====================================================================


To go from one to multiple dimensions, it is tempting to just extend the one
dimensional discretisation. For example, starting with the conservation law

\begin{equation}
	\deldt{\U} + \deldx{\F(\U)} + \frac{\del}{\del y} \mathbf{G}(\U) = 0
\end{equation}


where $\F$ is the hyperbolic flux in $x$ direction and $\mathbf{G}$ is the
hyperbolic flux in $y$ direction (see e.g.
Eq.~\ref{eq:euler-dimensional-split}) and just apply e.g. Godunov's finite
volume method:

\begin{equation}
\U_{i,j}^{n+1} =
	\U_{i,j}^n +
	\frac{\Delta t}{\Delta x}
	\left(
		\F_{i - \half, j} - \F_{i + \half, j}
	\right)
	+ \frac{\Delta t}{\Delta x}
	\left(
		\mathbf{G}_{i ,j - \half} - \mathbf{G}_{i, j + \half}
	\right)
\end{equation}


However, this is a bit of a problem. The upwinding here is not complete.
To explain, consider the 2D advection equation

\begin{equation}
	\deldt{q} + v_x \deldx{q} + v_y \frac{\del}{\del y} q = 0
\end{equation}

with constant coefficients $v_x$ and $v_y$. Now suppose we have advecting
velocities $v_x = v_y = 1$, i.e. the advection velocity is along the diagonal.
Then our method reads 

\begin{equation}
q_{i,j}^{n+1} =
	q_{i,j}^n +
	v_x \frac{\Delta t}{\Delta x}
	\left(
		q_{i - \half, j} - q_{i + \half, j}
	\right)
	+ v \frac{\Delta t}{\Delta x}
	\left(
		q_{i ,j - \half} - q_{i, j + \half}
	\right)
\end{equation}

This expression doesn't involve $q_{i-1, j-1}$ at all, but that's actually the
diagonal value that should be advected to $q_{i, j}$ in the next timestep!


One way of doing things is to actually formulate more sophisticated unsplit
methods that involve the appropriate stencils. We shan't do that here though.
We make use of dimensional splitting. Instead of solving

\begin{equation}
\begin{cases}
\text{PDE: } &
	\deldt{\U} + \deldx{\F(\U)} + \frac{\del}{\del y} \mathbf{G}(\U) = 0
\\
\text{IC: } &
	\U(x, y, t^n) = \U^n
\end{cases}
\end{equation}

we do it in 2 steps (3 for 3D):

\textbf{Step 1}: We obtain an intermediate result $\U^{n+\half}$ by solving the
``x - sweep'' over the \textbf{full} time interval $\Delta t$ :

\begin{equation}
\begin{cases}
	\text{PDE: } & \deldt{\U} + \deldx{\F(\U)} = 0\\
	\text{IC: } &  \U = \U^n
\end{cases}
\end{equation}

\textbf{Step 2}: We evolve the solution to the final $\U^{n+1}$ by solving the
``y - sweep'' over the \textbf{full} time interval $\Delta t$ :

\begin{equation}
\begin{cases}
\text{PDE: } &
	\deldt{\U} + \frac{\del}{\del y} \mathbf{G}(\U) = 0
\\
\text{IC: } &
	\U = \U^{n+\half}
\\
\end{cases}
\end{equation}

using the 1D methods that are described.
This is called ``Strang splitting'' and gives us a first order accurate method.

For a second order accurate method, we need to do one more step in 2D:

\begin{enumerate}
	\item Get $\U^{n + 1/4}$ by doing an x - sweep over the time interval $\Delta t / 2$
	\item Get $\U^{n + 3/4}$ by doing an y - sweep over the time interval $\Delta t$ and using the intermediate solution $\U^{n + 1/4}$
	\item Get $\U^{n + 1}$ by doing an x - sweep over the time interval $\Delta t / 2$ and using the intermediate solution $\U^{n + 3/4}$
\end{enumerate}



However, if $\Delta t$ is kept constant over multiple time steps, which is
often the case for linear advection, we can get the first order method
described above to be second order accurate by switching the order of the
sweeps every time step (see \cite{leveque_2002}), i.e. if for one time step we
did the x-sweep first, in the next one we do the y-sweep first, then in the
next time step we do the x-sweep first again, and so on. The order of the
sweeps doesn't matter as long as all sweeps have been done in the end, and by
alternating the order we recover the second order method formalism, but with a
twice as big time step.




