\newpage
%===============================================================================
\section{Developer Notes}
%===============================================================================


%===============================================================================
\subsection{Adding New Files}
%===============================================================================

Behind the scenes, for every \verb|.cpp| file, we create an object file
(\verb|.cpp.o|) with \cmake. We do this by telling \cmake to create an ``object
library'' for any  pair of \verb|.cpp| and \verb|.h| files. We add them
manually to the \cmake build system by specifying that in the modify the
\verb|src/CMakeLists.txt| file.


For example, let's first look at the ``\verb|Logging|'' library. We have a file
\verb|Logging.cpp| and \verb|Logging.h|. In \verb|src/CMakeLists.txt|, we add
the library as follows:

\begin{lstlisting}
add_library(Logging OBJECT Logging.cpp Logging.h)
\end{lstlisting}

The library's name in \cmake's internal registry is then called
\verb|Logging|.

Our main executable, which has the name \verb|hydro| in \cmake's internals
(specified as \verb|add_executable(hydro src/main.cpp)| in
\verb|hydro_playground/CMakeLists.txt|), will need to have the \verb|Logging|
library linked against it. So we need to tell \cmake about that:

\begin{lstlisting}
target_link_libraries(hydro Logging)
\end{lstlisting}

And that should do the trick.

One more thing to note here is that the order of the link ``library''
inclusions (they're just object files, to be honest) is \emph{that the order
matters}. If object file/library \jargon{A} has a dependency \jargon{B} (for
example, \verb|Utils.cpp| requires \verb|Version.cpp| to be compiled \emph{and}
linked), you need to make sure to add the linking dependency \jargon{B}
\emph{after} \jargon{A}. For example:


\begin{lstlisting}
target_link_libraries(hydro A)
target_link_libraries(hydro B) # needed by A
\end{lstlisting}

The other way around will result in linking errors along the lines of:

\begin{lstlisting}
/usr/bin/ld: src/CMakeFiles/Utils.dir/Utils.cpp.o: in function `utils::print_header()': hydro-playground/src/Utils.cpp:41:(.text+0x134): undefined reference to `version::Version::MAJOR'
/usr/bin/ld: hydro-playground/src/Utils.cpp:42:(.text+0x140): undefined reference to `version::Version::MINOR'
/usr/bin/ld: hydro-playground/src/Utils.cpp:52:(.text+0x22a): undefined reference to `version::Version::GIT_BRANCH[abi:cxx11]'
/usr/bin/ld: hydro-playground/src/Utils.cpp:56:(.text+0x290): undefined reference to `version::Version::GIT_SHA1[abi:cxx11]'
\end{lstlisting}




% -----------------------------------------------------------------
\subsubsection{Libraries with other dependencies}
% -----------------------------------------------------------------

Some of the object files/libraries may require other libraries themselves. For
example, the \verb|Utils| library, defined in \verb|src/CMakeLists.txt| as

\begin{lstlisting}
add_library(Utils OBJECT Utils.cpp Utils.h)
\end{lstlisting}

also needs the \verb|Version| and the \verb|Logging| library linked against it.
We then simply need to add the dependency using the same syntax as for the
executable \verb|hydro| above, and just change the target:

\begin{lstlisting}
target_link_libraries(Utils Version)
target_link_libraries(Utils Logging)
\end{lstlisting}





% -----------------------------------------------------------------
\subsubsection{\texttt{Version.cpp} and \texttt{Config.h}}
% -----------------------------------------------------------------

Currently, there are two exceptions to this procedure. Those are the files
\verb|Version.cpp| and \verb|Config.h|. They are special because they will be
generated with \cmake from their respective templates, \verb|src/Config.h.in|
and \verb|src/Version.cpp.in|.

The generated files will be \verb|your_build_dir/Version.cpp| and
\verb|your_build_dir/Config.h|.  So to get the \verb|Version| library to
compile, we need to tell it a) where to find the file, and b) that the header
file that needs to be included is in a different directory. We do that as
follows:


\begin{lstlisting}
add_library(Version "${CMAKE_BINARY_DIR}/Version.cpp" Version.h)
target_include_directories(Version PUBLIC "${CMAKE_CURRENT_SOURCE_DIR}")
\end{lstlisting}

\verb|${CMAKE_BINARY_DIR}| is the directory you're currently building the
project in. The \verb|${CMAKE_CURRENT_SOURCE_DIR}| variable gives you the path
to the directory where the \verb|CMakeLists.txt| file is located, which is
conveniently the same directory as the \verb|Version.h| header file.



Similarly, if you want a library to include the \verb|Config.h| header, you
need to tell it where it is as follows. Take for example the library
\verb|Utils| again:

\begin{lstlisting}
add_library(Utils Utils.cpp Utils.h)
target_include_directories(Utils PUBLIC "${PROJECT_BINARY_DIR}")
\end{lstlisting}





%===============================================================================
\subsection{Tests}
%===============================================================================

%===============================================================================
\susubbsection{Adding Tests}
%===============================================================================

- how to add tests

- how to run tests

- what tests do

- CI

